Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-20 sec_results.tex
update on sec 5.2

To further observe the behavior of the ridge yield with respect to the hard process, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}. The ridge structures are still seen with the event scale selection. With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.

@@

The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$ (left) or $\ptjet$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield increases as the event scale increases by requiring higher $\ptlead$ (left) or $\ptjet$. The model comparisons are are shown for $\pythiashoving$ with a blue and $\pythiam$ with a red line. The $\pythiashoving$ describes ridge yield with the selection. $\pythiam$ predicts non ridge yield with the selection, which also tell there is little ignore-able jet contamination. Both models well describe the away-side yield with the $\ptjet$ selection and overestimates away-side yield with the $\ptlead$ selection.

@@

The spectra of the ridge yield as function of the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) are shown in Fig.~\ref{fig:RidgeYield_ESE}. The spectra are compared with model predictions. 
The increases of ridge yield with the selections are observed and the model with PYTHIA8 + String Shoving underestimates the ridge yield. with the $\it{p}_{\rm{T, Jet}}$ selection. the model prediction with PYTHIA8 default still assures ignorable jet contamination.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
	\label{fig:RidgeYield_ESE}
\end{figure}

>>>>

To further observe the behavior of the event scale dependent ridge yield, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection. In Fig.~\ref{fig:PlotCorrHMTSel}, The ridge structures are still seen with the event scale selection. With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which come from the limited jet acceptance.

@@

The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$(lower) or $\ptjet$(upper) is shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield increases as the event scale increases by requiring higher $\ptlead$ or $\ptjet$ from the unbiased events, which corresponds to the plot in the most left upper panel. The model comparisons are shown for $\pythiashoving$ with a blue and $\pythiam$ with a orange line. The $\pythiashoving$ qualitatively describes the near-side peak with the event scale selection. On the other hand, $\pythiam$ does not predicts the near-side peak with the event scale selection, which also tell there is ignorable jet contamination. Both models well describe the away-side yield with the $\ptjet$ selection and overestimates away-side yield with the $\ptlead$ selection.

@@

The spectra of the ridge yield as function of the minimum $\ptlead$(left) or$\ptjet$(right) selection are shown in Fig.~\ref{fig:RidgeYield_ESE}. The measured spectra show that the ridge yield increases with the increasing selection requirement. The spectra are compared with the model predictions. $\pythiashoving$ predict the ridge yield with the event scale selection. $\pythiashoving$ underestimates the ridge yield with the increasing event scale selection. $\pythiam$ does not predict the ridge yield estimating zero yield, which also imply the ignorable jet contamination into the ridge yield.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
	\caption{The ridge yield spectra with respect to the leading particle and jet selections. The filled circles show measurement with ALICE. Model predictions are compared with measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
	\label{fig:RidgeYield_ESE}
\end{figure}
